---
title: "project2"
output: html_document
---

```{r}
library(tidyverse)
library(tidytuesdayR)
```

# Fun with functions

## Part 1A: Exponential transformation

Write a function that computes the exponential of a number using the truncated series expansion. The function should take two arguments:

x: the number to be exponentiated

k: the number of terms to be used in the series expansion beyond the constant 1. The value of k is always  ≥1.

For example, if 𝑘 =1, then the Exp function should return the number 1 +𝑥. If 𝑘 =2, then you should return the number 1 +𝑥 +𝑥2/2!.

Include at least one example of output using your function.
```{r}
Exp <- function(x, k) {
  ex <- 1
  for (i in 1:k){
    ex <- ex + ((x^i)/factorial(i))
  }
  return(ex)
}
```

```{r}
Exp(2,567)
```

## Part 1B: Sample mean and sample standard deviation

Next, write two functions called sample_mean() and sample_sd() that takes as input a vector of data of length 𝑁 and calculates the sample average and sample standard deviation for the set of 𝑁 observations.

Include at least one example of output using your functions.

```{r}
myvector <- c(4,5,67,1,3,4,5)
sample_mean <- function(x) {
    add <- 0
    for (i in x) {
      add <- add + i
    }
    return(add/length(x))
}

sample_mean(myvector)
```

```{r}
sample_sd <- function(x) {
    add <- 0
    for (i in x){
      add <- add + ((i-sample_mean(x))^2)
    }
    return(sqrt((1/(length(x)-1))*add))
}

sample_sd(myvector)
```

## Part 1C: Confidence intervals

```{r}
calculate_CI <- function(x, conf) {
    alpha <- 1 - conf
    degrees_freedom <- length(x) - 1
    t_score <- qt(p = alpha / 2, df = degrees_freedom, lower.tail = FALSE)
    
    lower_bound <- sample_mean(x)-(t_score*sample_sd(x)/sqrt(length(x)))
    upper_bound <- sample_mean(x)+(t_score*sample_sd(x)/sqrt(length(x)))
    ci<- c(lower_bound,upper_bound)
    
    return(ci)
}

calculate_CI(myvector, 0.95)
calculate_CI(myvector, 0.82)
```

```{r} 
#test
dat <- data.frame(x = myvector)
fit <- lm(myvector ~ 1, dat)

# Calculate a 95% confidence interval
confint(fit, level = 0.95)

#test #2
dat <- data.frame(x = myvector)
fit <- lm(myvector ~ 1, dat)

# Calculate a 95% confidence interval
confint(fit, level = 0.82)
```

# Part 2: Wrangling data


```{r}
library(here)
if (!file.exists(here("data", "tuesdata_rainfall.RDS"))) {
    tuesdata <- tidytuesdayR::tt_load("2020-01-07")
    rainfall <- tuesdata$rainfall
    temperature <- tuesdata$temperature

    # save the files to RDS objects
    saveRDS(tuesdata$rainfall, file = here("data", "tuesdata_rainfall.RDS"))
    saveRDS(tuesdata$temperature, file = here("data", "tuesdata_temperature.RDS"))
}
```

```{r}
rainfall <- readRDS(here("data", "tuesdata_rainfall.RDS"))
temperature <- readRDS(here("data", "tuesdata_temperature.RDS"))

glimpse(rainfall)
glimpse(temperature)
```
```{r}
rainfall <- rainfall %>%
  drop_na()%>%
  mutate(date = ymd(paste0(year,"-",month,"-",day)),
         city_name = toupper(city_name))%>%
  select(!c(month,day))

raintemp <- inner_join(rainfall, temperature, by = c("city_name", "date"))

raintemp

```

# Part 3: Data visualization

## Part 3A: Plotting temperature data over time

```{r}
p <- raintemp %>%
  filter(year >= 2014)%>%
  group_by(city_name,year)%>%
  summarize(
    maxtemp = max(temperature),
    mintemp = min(temperature)
  )
p %>%
  ggplot(aes(x = year))+
  geom_line(aes(y = maxtemp, color = "maxtemp"))+
  geom_line(aes(y = mintemp, color = "mintemp"))+
  facet_wrap(~ city_name, nrow = 2, axes = "all")+
  labs(
    title = "Maximum and Minimum Temperature in Each City per Year",
    subtitle = "Maximum and minimum temperatures remain steady through the years.",
    x = "Year",
    y = "Temperature(˚C)",
    color = "",
    caption = "SOURCE: #tidytuesday project"
  )+
  scale_color_manual(
      values = c("hotpink", "purple"),           # Custom colors
    labels = c("Maximum temperature", "Minimum temperature") 
  )+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Part 3B: Plotting rainfall over time

I began with the error messages if the inputted data doesn't exist in the data to stop any errors. Then, I filtered the data by city and year, and then plotted the graph. Lastly, I added aesthetic choices to make the graph more reader friendly.
```{r}
rainplot <- function(cty, yr) {
  if (!cty %in% raintemp$city_name){
    stop("City does not exist in dataset.")
  }
  if (!yr %in% raintemp$year){
    stop("Year does not exist in the dataset.")
  }
  raintemp%>%
    filter(city_name == cty, year == yr)%>%
    ggplot(aes(log(rainfall)))+
    geom_histogram(bins = 30)+
    labs(
      title = paste0("Distribution of Rainfall in ",yr),
      subtitle = paste0("City: ", cty),
      x = "Log(Rainfall (mm))",
      y = "Frequency",
      caption = "SOURCE = #tidytuesday project"
    )  
  
    
}

rainplot(cty = "SYDNEY", yr = 2017)
```
