---
title: "project2"
output: html_document
---

```{r}
library(tidyverse)
library(tidytuesdayR)
```

# Fun with functions

## Part 1A: Exponential transformation

Write a function that computes the exponential of a number using the truncated series expansion. The function should take two arguments:

x: the number to be exponentiated

k: the number of terms to be used in the series expansion beyond the constant 1. The value of k is always  ≥1.

For example, if 𝑘 =1, then the Exp function should return the number 1 +𝑥. If 𝑘 =2, then you should return the number 1 +𝑥 +𝑥2/2!.

Include at least one example of output using your function.
```{r}
Exp <- function(x, k) {
  ex <- 1
  for (i in 1:k){
    ex <- ex + ((x^i)/factorial(i))
  }
  return(ex)
}
```

```{r}
Exp(2,567)
```

## Part 1B: Sample mean and sample standard deviation

Next, write two functions called sample_mean() and sample_sd() that takes as input a vector of data of length 𝑁 and calculates the sample average and sample standard deviation for the set of 𝑁 observations.

Include at least one example of output using your functions.

```{r}
myvector <- c(4,5,67,1,3,4,5)
sample_mean <- function(x) {
    add <- 0
    for (i in x) {
      add <- add + i
    }
    return(add/length(x))
}

sample_mean(myvector)
```

```{r}
sample_sd <- function(x) {
    add <- 0
    for (i in x){
      add <- add + ((i-sample_mean(x))^2)
    }
    return(sqrt((1/(length(x)-1))*add))
}

sample_sd(myvector)
```
